Saturday mornings with Tufte

### 2022-02-08 _posts/2022-02-05-saturday-mornings-with-tufte/saturday-mornings-with-tufte.Rmd
Add categories

---
title: "Saturday mornings with Tufte"
description: |
  The other half of data science skillbuilding
author:
  - name: Steve Linberg
    url: https://slinberg.net
date: 2022-02-05
output:
  distill::distill_article:
    self_contained: false
preview: tuftebooks.jpg
---

>>>>

---
title: "Saturday mornings with Tufte"
description: |
  The other half of data science skillbuilding
author:
  - name: Steve Linberg
    url: https://slinberg.net
date: 2022-02-05
output:
  distill::distill_article:
    self_contained: false
preview: tuftebooks.jpg
categories:
  - tufte
  - design
---
